---
title: "What Kind of Taxi Driver are You?"
author: "Fausto"
date: "4/27/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
use_virtualenv("root") #name the enviornment from conda to use
```

## What are we trying to do?

At the TLC we've studied driver income to inform policy legislation. Recently legislation passed on xyz. Looking back at 2013 there is public data available to test similar theories on driver types. We will begin this analysis with a look through the data and some basic calculations. Let's begin. 

```{r}
library(data.table)
library(fasttime)
library(dplyr)
library(fst)

#releavant cols
trip_cols = c('medallion', 'hack_license',
              'pickup_datetime','dropoff_datetime',
              'trip_time_in_secs', 'trip_distance')
fare_cols = c('medallion', 'hack_license',
              'pickup_datetime','fare_amount',
              'surcharge')

#read data
trips = read.fst('C:/Users/0000/Documents/trip_1.fst',
                 as.data.table = T,
                 from =1,
                 to = 100000,
                 columns = trip_cols)

trips_fare = read.fst('C:/Users/0000/Documents/trip_fare_1.fst',
                 as.data.table = T,
                 from =1,
                 to = 1000000,
                 columns = fare_cols)
```


We merge the data to create one table that's easier to work with:

```{r}
trips = merge(trips,
              trips_fare,
              by = c("medallion", "hack_license","pickup_datetime"),
              all.x = T)
```

Now we can begin to put together the statistics we believe represent a type of driver. Amount of hours worked can be very informative. we can start with pickup hours which are the unique count of hours a driver works:

```{r}
trips_agg =
trips[
  ,.(hours_per_day = uniqueN(substr(pickup_datetime,1,13)),
     total_income = sum(fare_amount) + sum(surcharge),
     total_distance = sum(trip_distance),
     total_trip_hours = sum(trip_time_in_secs)/60
     ),
  .(hack_license,
    day = substr(pickup_datetime,1,10))]
```

We can look at the distribution of work and other important factors:

```{r}
summary(trips_agg)
```

So how do we try and group drivers? We moved onto KNN. Caret is solid in R, but why not use the time to practice some python? I ran the machine learning process in python's scikit-learn. We start by extracting the 




```{python}
import os
os.environ['QT_QPA_PLATFORM_PLUGIN_PATH'] = 'C:/Users/0000/Anaconda3/Library/plugins/platforms'
import numpy as np
import pandas as pd
import scipy.stats as stats
import matplotlib.pyplot as plt
import sklearn
from sklearn.model_selection import train_test_split
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
